Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-03 SWoPP2018 Paper/paper.tex
Added second affiliation for sensei
Reordered affliations and changed section title.

\affiliate{TiTech}{Tokyo Institute of Technology, 
Meguro, Tokyo 152--8550, Japan}
\affiliate{TUDelft}{Delft University of Technology, Mekelweg 2, 2628 CD Delft, Netherlands}

\author{Erwin de Haan}{TiTech,TUDelft}[e.r.dehaan@student.tudelft.nl]
\author{Artur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
\author{Satoshi Matsuoka}{TiTech}[matsu@is.titech.ac.jp]

@@

\subsection{Network Tested + Data-set}

@@

\begin{table}[h]
  \centering
  \caption{FPGA Kernel performance}\label{tab:kernel-performance}
  \begin{tabular}{llll}
    \toprule
    \textbf{Block size} & \textbf{GFLOPS MNIST}  & \textbf{GFLOPS CIFAR-10}  \\
    \midrule
    64$\times$64 & \num{17.8} & \num{18.9}  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
    16$\times$16 & \num{4.3} & \num{4.4} \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\affiliate{TiTech}{Tokyo Institute of Technology, 
Meguro, Tokyo 152--8550, Japan}
\affiliate{TUDelft}{Delft University of Technology, Mekelweg 2, 2628 CD Delft, Netherlands}
\affiliate{Riken}{RIKEN Center for Computational Science, Chuo-ku, Kobe, Hyogo 650-0047 Japan}

\author{Erwin de Haan}{TiTech,TUDelft}[e.r.dehaan@student.tudelft.nl]
\author{Artur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
\author{Satoshi Matsuoka}{TiTech,Riken}[matsu@is.titech.ac.jp]

@@

\subsection{Test Networks and Inputs}

@@

\begin{table}[h]
  \centering
  \caption{FPGA Kernel performance}\label{tab:kernel-performance}
  \begin{tabular}{lSS}
    \toprule
    \textbf{Block size} & \textbf{GFLOPS MNIST}  & \textbf{GFLOPS CIFAR-10}  \\
    \midrule
    64$\times$64 & 17.8 & 18.9  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
    16$\times$16 & 4.3 & 4.4 \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
    \bottomrule
  \end{tabular}
\end{table}
